Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-03-18 submission/manuscript.rmd
fix line width for readability

- **IBM MarketScan Medicare Supplemental Database (MDCR)** is a claims database representing retirees in the United States with primary or Medicare supplemental coverage
- **Optum De-Identified Clinformatics® Data Mart Database – Date of Death (Optum-DOD)** is a claims database including members of private health insurance.

- **Optum de-identified Electronic Health Record Dataset (Optum-EHR)** is an EHR database including Humedica’s Electronic Health Record.

@@

<!-- Need to fix the numbers. See icpe abstract -->
A total of `r sum(incidenceOverall$maxTreatment) + sum(incidenceOverall$maxComparator)` patients were initially considered for our analyses. Of those, `r sum(incidenceOverall$maxTreatment)` received teriparatide and `r sum(incidenceOverall$maxComparator)` received an oral bisphosphonate \@ref(tab:table1).

>>>>

- **IBM MarketScan Medicare Supplemental Database (MDCR)** is a claims database
  representing retirees in the United States with primary or Medicare
supplemental coverage.
- **Optum De-Identified Clinformatics® Data Mart Database – Date of Death
  (Optum-DOD)** is a claims database including members of private health
insurance.
- **Optum de-identified Electronic Health Record Dataset (Optum-EHR)** is an
  EHR database including Humedica’s Electronic Health Record.

@@

<!-- Need to fix the numbers. See icpe abstract -->
A total of `r sum(incidenceOverall$maxTreatment) +
sum(incidenceOverall$maxComparator)` patients were initially considered for our
analyses. Of those, `r sum(incidenceOverall$maxTreatment)` received
teriparatide and `r sum(incidenceOverall$maxComparator)` received an oral
bisphosphonate (Table\@ref(tab:table1)).
